---
title: "The Big Bang Theory Viewership Report"
author: "Chen Ye"
date: "2025-04-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## 📺 Show Description

*The Big Bang Theory* is an American television sitcom created by Chuck Lorre and Bill Prady. The show premiered on CBS on **September 24, 2007**, and concluded on **May 16, 2019**, airing a total of **279 episodes** over **12 seasons**.

The story revolves around five characters living in Pasadena, California:
- **Leonard Hofstadter** and **Sheldon Cooper**, both brilliant physicists working at Caltech,
- **Penny**, an aspiring actress and waitress from Nebraska,
- **Howard Wolowitz**, an aerospace engineer,
- and **Raj Koothrappali**, an astrophysicist.

The show humorously explores their social awkwardness, romantic relationships, and love for science and pop culture, making it one of the most successful sitcoms of the 21st century.


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
